### 2023-11-09 manuscript/manuscript.Rmd
add 'biological origin' to the abstract
replace 'pre-ionisation' with 'precursor'

We present a data-driven ensemble approach for the ‘first pass’ automated assignment of molecular formulas to mass spectra acquired from high-resolution electrospray ionisation mass spectrometry (ESI-MS). This is primarily intended for metabolomics experiment data using non-targeted metabolome fingerprinting and LC-MS profiling.
The approach incorporates the use of *m/z* correlation networks, molecular formula generation and selection as well as graphically based component plausibility selection to assign molecular formulas to *m/z* features.
The R package *assignments* was developed as a user-friendly implementation of the approach and is freely available from https://github.com/aberHRML/assignments.
The approach was tested in a mix of known chemical standards, human urine samples spiked with the chemical standards mix and a data set comparing leaf tissue samples of different ecotypes of the model grass species *Brachypodium distachyon*. 
Of the `r compounds_possible` chemical standards that had theoretical ionisation products matching *m/z* features in the standards mix, the approach assigned `r compounds_percent_assigned$standards`% of these.
Across the example matrices, an average of `r average_percent_assigned`% of the *m/z* features were assigned a molecular formula matching an average of `r average_kegg_compounds` compounds in the KEGG compound database.

@@

Possible adduct, isotopic and transformation mass relationships were calculated for each pair of correlated *m/z*.
The pre-ionisation masses ($M$) were first calculated for all adduct, isotopic and transformation combinations for each of the *m/z*. 
An $M$ for a given ionisation product *m/z*, adduct, isotope and transformation was calculated using the following equation:

>>>>

We present a data-driven ensemble approach for the ‘first pass’ automated assignment of molecular formulas to mass spectra acquired from high-resolution electrospray ionisation mass spectrometry (ESI-MS). This is primarily intended for metabolomics experiment data of biological origin, using non-targeted metabolome fingerprinting and LC-MS profiling.
The approach incorporates the use of *m/z* correlation networks, molecular formula generation and selection as well as graphically based component plausibility selection to assign molecular formulas to *m/z* features.
The R package *assignments* was developed as a user-friendly implementation of the approach and is freely available from https://github.com/aberHRML/assignments.
The approach was tested in a mix of known chemical standards, human urine samples spiked with the chemical standards mix and a data set comparing leaf tissue samples of different ecotypes of the model grass species *Brachypodium distachyon*. 
Of the `r compounds_possible` chemical standards that had theoretical ionisation products matching *m/z* features in the standards mix, the approach assigned `r compounds_percent_assigned$standards`% of these.
Across the example matrices, an average of `r average_percent_assigned`% of the *m/z* features were assigned a molecular formula matching an average of `r average_kegg_compounds` compounds in the KEGG compound database.

@@

Possible adduct, isotopic and transformation mass relationships were calculated for each pair of correlated *m/z*.
The precursor masses ($M$) were first calculated for all adduct, isotopic and transformation combinations for each of the *m/z*. 
An $M$ for a given ionisation product *m/z*, adduct, isotope and transformation was calculated using the following equation:
